Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-11-05 update-10-22/update-10-22.tex
Added citations for natural death rates.
Finalized ode model

%imports
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{url}

@@

\section{Model Setup}

>>>>

%imports
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{url}
\usepackage{hyperref}

@@

\section{Model Setup}
	We estimate the non-COVID death rate $\mu$ using the average United States death rate in urban regions from 2019 \cite{death-trends}.
	That is, $\mu = 1.8997 \times 10^{-5}$ [per day].

	\begin{table}[h]
		\centering
		\caption{Time sequence of events and simulation times.}
		\label{tab:times}
		\begin{tabular}{ c c c c }
			\hline
			\hline
			Initial simulation time	&	Imposed lockdown	&	Effective lockdown	&	Last fitting day	\\
			\hline
			March 18, 2020	&	March 21, 2020	&	 April 1, 2020	&	June 24, 2020	\\
			$t_i = 1$	&	$t_q = 4$	&	$t_q = 15$	&	$t_f = 99$ \\
			\hline
			\hline
		\end{tabular}
	\end{table}
